Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-06 cross_compilation.tex
finished fabric

SHORT INTRO. EXPLAIN A FEW USECASES FOR FABRIC. E.G. REBOOT, INSTALL PACKAGE, RUN SCRIPT ON MULTIPLE RASPIS. COPY FILES TO/FROM PC AND MULTIPLE RASPIS

% Exit chroot, umount, and write to memory card
\begin{lstlisting}[]
from fabric.api import run, env, task
# Python Fabric script to run commands on multiple hosts through ssh
#
# Run script as 'fab <task>', where <task> is one of the scripts functions
# marked as a tesk. The task marked as 'default' will be run if <task> is not
# specified

@@

@task
def install(program):
    """
    Install a program
    program: program name
    """
    result = run('apt-get install -y {}'.format(program), quiet=True)

@task
def copy_to_rasp(filename):
    put(...)

@@

execute a script function by calling "fab install:feh"

>>>>

Controlling multiple devices using \ac{SSH} from a single \ac{PC}
often leads to a lot of repetitive work. E.g.

\begin{itemize}
    \item rebooting a set of devices
    \item installing applications in multiple devices
    \item copy files to/from multiple devices
    %\item run a script in multiple devices
\end{itemize}

\texttt{Fabric} provides a python library to ease the task of working
with multiple devices from a single \ac{PC}. The code below provides
a small script that can perform the few items above:

%SHORT INTRO. EXPLAIN A FEW USECASES FOR FABRIC. E.G. REBOOT, INSTALL PACKAGE, RUN SCRIPT ON MULTIPLE RASPIS. COPY FILES TO/FROM PC AND MULTIPLE RASPIS

% Exit chroot, umount, and write to memory card
\Suppressnumber\begin{lstlisting}[]
<@\textcolor{gray}{\$CODEDIR/fabfile.py}@>
<@\textcolor{gray}{
-------------------------------------------}
\Reactivatenumber @>
from fabric.api import run, env, task
# Python Fabric script to run commands on multiple hosts through ssh
#
# Run script as 'fab <task>', where <task> is one of the scripts functions
# marked as a tesk. The task marked as 'default' will be run if <task> is not
# specified

@@

@task
def reboot():
    """ Reboot device """
    sudo('reboot', quiet=True)

@task
def install(program):
    """
    Install a program
    program: program name
    """
    result = sudo('apt-get install -y {}'.format(program), quiet=True)
    print(result)

@task
def push(src,dst):
    """
    Copy file to device
    src: source file path
    dst: destination file path
    """
    put(src, dst)

@@

The script functions can be called from the command shell in the following
manner. Notice how fab automatically searches the directory for a file 
named 'fabfile.py' and how fab is called with function name and arguments
'fab <FUNCTION>:arg1,arg2,...:
\begin{lstlisting}[]
$ fab reboot
$ fab install:tmux
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

\begin{lstlisting}[]
$ fab reboot
$ fab install:tmux
$ fab push:"${CODEDIR}/hello_world",'~/'
[192.168.87.107] Executing task 'push'
[192.168.87.107] put: /home/<USER>/code/hello_world -> /home/pi/hello_world

Done.
Disconnecting from 192.168.87.107... done.
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

%execute a script function by calling "fab install:feh"
